2020 U.S. Presidential Election Forecast

### 2024-03-15 paper/paper.qmd
added figure for state

@fig-distribution-by-age-group, @fig-distribution-by-gender, @fig-distribution-by-race, and @fig-distribution-by-education illustrate comparisons between survey data and post-stratification data across different variables. In these visuals, orange bars represent post-stratification data, while green bars signify survey data. The percentages displayed on each figure are rounded to the nearest tenth, introducing a potential margin of error of ±0.1% in the total values. Generally, the survey data aligns closely with the post-stratification data, maintaining a discrepancy of about 10% across most categories. Notable exceptions are observed in the '30-49' age group and the 'Some college' education level, where the differences exceed this margin.

```{r}
# insert figure for state here
```

@@

@tbl-voters-intention-to-vote-for-trump shows the proportion of voters who intend to vote for Donald Trump or not. Also, @tbl-voters-intention-of-their-primary-party shows the proportion of voters' supporting party. The data used to create these table is from the @citeSurveyData. We see that Donald Trump and his party Republican are not expected to win the popular vote before we implement the model.

>>>>

@fig-data-distribution-by-state, @fig-distribution-by-age-group, @fig-distribution-by-gender, @fig-distribution-by-race, and @fig-distribution-by-education illustrate comparisons between survey data and post-stratification data across different variables. In these figures, orange bars represent post-stratification data, while green bars signify survey data. The percentages displayed on each figure are rounded to the nearest tenth, introducing a potential margin of error of ±0.1% in the total values. Generally, the survey data aligns closely with the post-stratification data, maintaining a discrepancy of about 10% across most categories. Notable exceptions are observed in the '30-49' age group and the 'Some college' education level, where the differences exceed this margin.

```{r fig.width=8.5, fig.height=6}
#| message: false
#| echo: false
#| warning: false
#| label: fig-data-distribution-by-state
#| fig-cap: Distribution of Sample and Population by State
# Read in the survey data
survey_data <- cleaned_data_survey

state_survey <- survey_data %>% 
  group_by(state) %>% 
  summarise(n = n()) %>% 
  mutate(pct = n/sum(n), type = "Survey",
         group = "state")

state_post_strat <- post_strat_data %>% 
  group_by(state) %>% 
  summarise(n = n()) %>% 
  mutate(pct = n/sum(n), type = "Post-Strat",
         group = "state")

variables <- rbind(state_survey, state_post_strat)

# plot our results, grouped by variable with each line representing
# the proportions for the polling and post-strat data

variables %>% ggplot(aes(as.factor(state), pct, group=as.factor(type), linetype = as.factor(type))) + 
  geom_line() + 
  facet_wrap(~group, ncol = 1, scales = "free_x") + 
  theme(axis.text.x = element_text(angle=90, hjust = 1, vjust = 0.5)) + # Corrected theme function
  labs(x = "State", y = "Proportion", linetype = "Data Set",
       title = "Distribution of Sample and Population by State") +
  scale_y_continuous(labels = scales::percent)

@@

@tbl-voters-intention-to-vote-for-trump shows the proportion of voters who intend to vote for Donald Trump or not. Also, @tbl-voters-intention-of-their-primary-party shows the proportion of voters' supporting party. The data used to create these table is from the Democracy Fund + UCLA Nationscape [@citeSurveyData]. We see that Donald Trump and his party Republican are not expected to win the popular vote before we implement the model.
